 
\documentclass[margin,11pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\address{ {\bf Andrew Johnson} \\ contact@karmafeeder.com \\ (301) 466-4720 }

\begin{resume}
 
\section{OBJECTIVE}  A full-time position in the field of software development.


\section{EXPERIENCE}      {\bf Scoopler Inc., San Francisco, CA} \\
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Software Consultant} & January 2011 -- March 2011 (3 months) 
                \end{ncolumn}
                Web Development with Python Django.
 
                {\bf MSU Wireless Networking Lab, Bozeman, MT} \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Research Assistant} & November 2009 -- July 2010 (9 months)
                \end{ncolumn}
                Worked with Dr. Jian Tang to develop wireless network 
                routing algorithms \& simulations. Network models were 
                built using linear programming in C++

                {\bf Flux Corporation, Billings, MT} \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                \underline{Software Developer Intern} & March 2007 -- May 2007 (3 months)
                \end{ncolumn}
                Web Development with Java Server Pages.

\section{EDUCATION}  Computer Science, Montana State University, 2010
 
\section{HONORS}
    Winning team of local ACM Programming Competition 2008. Travelled to regional competition in Salt Lake, UT.
    
    Upper level coursework including the capstone course in compilers completed as a first year student.
    
    Completed 3 years of college-level Japanese courses with plans to pass Japanese Language Proficiency Test N1 Certification.
    
    Recipient of MSU Presidential Scholarship, four year financial award based on high SAT scores.
 
\section{PORTFOLIO} http://karmafeeder.com \\
                    http://gityou.com

\section{EXPERTISE} C, C++, Erlang, Haskell, Java, Javascript, ML, Python, SQL, Git, Linux, Django, Tornado, RabbitMQ, XHTML, CSS, jQuery, Linear Programming, Information Retrieval, Recommender Systems

\end{resume} 
\end{document}





